SAT Competition 2020\tnoteref{title}

### 2021-05-06 paper/main.tex
one cite

The focus of the traditional Main track is on sequential SAT solvers and their evaluation on structured, non-random benchmarks coming from various application areas. To participate in the main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer. Moreover, the source code of the solver had to be made publicly available.

@@

In this section we provide a high-level overview of the results of SAT Competition 2020
%We focus on some interesting results.
Later on, we give more details about the solvers, including the key and new solving techniques
(Section~\ref{sec:winners}) and more in-depth analysis of the results (Section~\ref{sec:analysis}).

Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}),
performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
The four top solvers all have a different code base, which is rare and has not been observed for many years.
Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000-second limit.
Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.

@@

\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
The \solver{32} threaded variant received two awards in this competition: the overall third place and the third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for second-best performance on satisfiable instances. Interestingly, it 
at the same time exhibited  worst performance on unsatisfiable instances. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized initialization of branching heuristics~\cite{SC2020}.

@@

One can see that the VBS solves all the instances that
were solved by at least one solver and solves each instance in the best observed time.
By quantifying how much each participating solver contributes
to the performance of the VBS, we may attempt to establish which
technology (as represented by the solvers) is the most important
(and to what degree) in the observed state of the art of SAT solving.
We will here consider the following three related metrics conceptually derived
from the notion of VBS.
\begin{description}
\item[VBS1]
``The fastest takes it all'':
For each solver we count the number of times, it was the fastest to solve an instance.
\item[VBS2]
``Time aware, but proportional'':
A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
the following fraction of a point for solving $I$:
$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
\item[VBS3]
``Split the point for solving'':
We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
$\mathcal{S}_I$ is the set of solvers solving $I$.
\end{description}
We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
In the case of VBS3, where we discard the information about the solution times, 
we evenly split the one point reward for solving an instance to those solvers which were successful on it.

In contrast, VBS2 does not have this property as it in general distributes more than one point per instance.
Similarly to VBS1, it takes the solution time into account,
and similarly to VBS3 it does not award just the best solver on an instance.
For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
And, if all the solvers solve an instance with the same solution time,
each solver scores a whole point for that instance.

@@

\subsection{Greedy set cover}
Another perspective on how much each solver contributes to the state of the art
can be obtained by attempting to construct a sequential schedule of solvers 
(rather than relying on an oracle to pick one for each instance, as with VBS)
and looking at how big role each solvers plays in such a schedule. Since constructing 
an optimal schedule tends to be computationally hard, we start here by 
presenting a useful efficient alternative -- a greedy set cover approach.

With greedy set cover, we start with an empty schedule and iteratively consider 
each solver for the addition to the schedule obtained so far, picking the one
with the highest ``marginal contribution'' in terms of the number of problems
the new schedule will be able to solve. This is perhaps best demonstrated on
the actual data from the competition, again taking the Main track results.

@@

\subsection{Time-limited schedules}

@@

By employing a brute-force approach we first constructed a sequences of schedules 
where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
$i$ solvers and solves the highest number of instances under these constraints.
The results are presented in Table~\ref{tab:MainUniformTimeSplit}.
We can see that the initial increase from 264 to 278 of ``covered'' instances 
when using two solvers instead of one (although allowing each to only use half of the time)
does not continue further with additional solvers allowed,
although its still better to use three solvers in a fair time split 
(and cover 272 instances) than just one.
One could use this observation to conjecture that the really hard 
problems that were solved actually require quite a large time to 
get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
quickly diminishes.

We complemented this ``uniform time split'' schedule by formulating the schedule construction
problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
For each solver (and its configuration) $S$ we introduced an integer variable $R^S$ denoting 
the number of seconds $S$ will run in the new schedule. We then constructed a formula with the hard
constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one 
soft constraint for every instance $I$ of the form
\[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
(Note that while $R^S$ are variables, i.e.~unknowns, the $T^S_I$ are known constants in the formula.)

@@

Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
It is not clear to what degree is the obtained schedule unique and how much it relies on each solver being present and for how long.
Nevertheless, it is interesting to observe the total number of problems covered, here 286,
and compare it to the 278 achieved in Table~\ref{tab:MainUniformTimeSplit} with the uniform split and two solvers.

@@

The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is close to 40\% better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
We calculated the PAR-2 score for each VBS created from solver tuples in $P_k$. 
In Table~\ref{tab:tuples}, we report on the single best performing $k$-tuple $T_k \in P_k$ ($1 \leq k \leq 7$).

@@

Contributions to the VBS can be well captured by clustering the instance space into instance families. 
We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
and report their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculated the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the Main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

One big cluster that we identify consists of the \solver{Maple}-decedants, 
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a sub-cluster
with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
The high similarity suggest that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
use the same code-base as a lot of solvers in the \solver{Maple}-cluster, but their
overall performance is better and closer to the \solver{CMS}-cluster.
The three \solver{CMS} configurations
differ in their implementation of stochastic local search
(SLS) and have similar performance.
The 2020 version of \solver{CaDiCaL}
performed worse than the modifications based on the 2019 version and
does not quite fit into any cluster.

@@

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
The main result of the competition is the ranking of the solvers participating
in the Main track, according to their average PAR-2 score. To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:

@@

The 2020 SAT Competition successfully continued the tradition of the SAT Competition series. In 2020, significant advances
in SAT solver compared to previous years were observed. Some of the more interesting observations on the winning solving 
strategies include the following.
All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As can be seen in the \emph{Parallel} track, it appear difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track showed that it is worth integrating a full solver functionality in the incremental use-case.

>>>>

The focus of the traditional Main track is on sequential SAT solvers and their evaluation on structured, non-random benchmarks coming from various application areas. To participate in the Main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer. Moreover, the source code of the solver had to be made publicly available.

@@

In this section we provide a high-level overview of the results of SAT Competition 2020.
%We focus on some interesting results.
Later on, we give more details about the solvers, including the key and new solving techniques
(Section~\ref{sec:winners}) and more in-depth analysis of the results (Section~\ref{sec:analysis}).

Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids},
performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
The four top solvers all have a different code base, which is rare and has not been observed for many years.
Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
\solver{Relaxed-newTech} solved more instances within the 2000-second limit.
Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.

@@

\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
The \solver{32} threaded variant received two awards in this competition: the overall third place and the third best score on unsatisfiable instances. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup,Audemard:2014:LazyClauseExchange,Hamadi:2009:ManySat}.

@@

\solver{Painless Maple} received the award for second-best performance on satisfiable instances. 
Interestingly, \solver{Painless Maple}  
at the same time exhibits worst performance on unsatisfiable instances. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
It uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses and was submitted with two diversification variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized initialization of branching heuristics~\cite{SC2020}.

@@

One can see that the VBS solves all the instances that
were solved by at least one solver and solves each instance in the best observed time.
By quantifying how much each participating solver contributes
to the performance of the VBS, we may attempt to establish which
technology (as represented by the solvers) is the most important
(and to what degree) in the observed state of the art of SAT solving.
We consider here the following three related metrics conceptually derived
from the notion of VBS.

\begin{description}
\item[VBS-1]
``The fastest takes it all'':
For each solver we count the number of times, it was the fastest to solve an instance.
\item[VBS-2]
``Time aware, but proportional'':
A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
the following fraction of a point for solving $I$:
$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
\item[VBS-3]
``Split the point for solving'':
We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
$\mathcal{S}_I$ is the set of solvers solving $I$.
\end{description}

We remark that the sum of VBS-1 points, as well as VBS-3 points, computed across all the solvers
is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
This is obvious for VBS-1, as exactly one solver scores a point for solving an instance.
In the case of VBS-3, where we discard the information about the solution times, 
we evenly split the one point reward for solving an instance to those solvers which were successful on it.

In contrast, VBS-2 does not have this property as it in general distributes more than one point per instance.
Similarly to VBS-1, it takes the solution time into account,
and similarly to VBS-3 it does not award just the best solver on an instance.
For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
And, if all the solvers solve an instance with the same solution time,
each solver scores a whole point for that instance.

@@

\subsection{Greedy Set Cover}
Another perspective on how much each solver contributes to the state of the art
can be obtained by attempting to construct a sequential schedule of solvers 
(rather than relying on an oracle to pick one for each instance, as with VBS)
and looking at how big a role each solvers plays in such a schedule. Since constructing 
an optimal schedule tends to be computationally hard, we start here by 
presenting a useful efficient alternative -- a greedy set cover approach.

With greedy set cover, we start with an empty schedule and iteratively consider 
each solver for the addition to the schedule obtained so far, picking the one
with the highest ``marginal contribution'' in terms of the number of problems
the new schedule will be able to solve. We demonstrate this on
the actual data from the competition, again taking the Main track results.

@@

\subsection{Time-Limited Schedules}

@@

By employing a brute-force approach, we first construct a sequences of schedules 
where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
$i$ solvers and solves the highest number of instances under these constraints.
The results are presented in Table~\ref{tab:MainUniformTimeSplit}.
We can see that the initial increase from 264 to 278 of ``covered'' instances 
when using two solvers instead of one (although allowing each to only use half of the time)
does not continue further with additional solvers allowed,
although its still better to use three solvers in a fair time split 
(and cover 272 instances) than just one.
One could use this observation to conjecture that the really hard 
problems that were solved actually require quite a large time to 
get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
quickly diminishes.

We complement this ``uniform time split'' schedule by formulating the schedule construction problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
For each solver (and its configuration) $S$ we introduce an integer variable $R^S$ denoting the number of seconds $S$ runs in the new schedule. 
We then construct a formula with the hard constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one soft constraint for every instance $I$ of the form \[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
(Note that while $R^S$ are variables, i.e.~unknowns, the $T^S_I$ are known constants in the formula.)

@@

Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
Z3 comes up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
It is not clear to what degree is the obtained schedule unique and how much it relies on each solver being present and for how long.
Nevertheless, it is interesting to observe the total number of problems covered, here 286,
and compare it to the 278 achieved in Table~\ref{tab:MainUniformTimeSplit} with the uniform split and two solvers.

@@

The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is close to 40\% better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
We calculate the PAR-2 score for each VBS created from solver tuples in $P_k$. 
In Table~\ref{tab:tuples}, we report on the single best performing $k$-tuple $T_k \in P_k$ ($1 \leq k \leq 7$).

@@

Contributions to the VBS can be well captured by clustering the instance space into instance families. 
We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
and report their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculate the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the Main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

One big cluster that we identify consists of the \solver{Maple}-decedants, 
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a sub-cluster
with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
The high similarity suggests that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
use the same code-base as a lot of solvers in the \solver{Maple}-cluster, but their
overall performance is better and closer to the \solver{CMS}-cluster.
The three \solver{CMS} configurations
differ in their implementation of stochastic local search
(SLS) and have similar performance.
The 2020 version of \solver{CaDiCaL}
performs worse than the modifications based on the 2019 version and
does not quite fit into any cluster.

@@

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
The main result of the competition is the ranking of the solvers participating
in the Main track, according to their average PAR-2 score. To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}~\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:

@@

The 2020 SAT Competition successfully continues the tradition of the SAT Competition series. In 2020, significant advances
in SAT solvers compared to previous years are observed. Some of the more interesting observations on the winning solving 
strategies include the following.
All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As can be seen in the \emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.
